### 2019-03-26 Rapport/TG_ITA/Bibliographic_analysis/Coursera-v2.tex
Week 4 assignment

	\begin{equation}
	x_{0} = (feature)
	\end{equation}
	\begin{equation}
	x_{1} = (feature)^{2}
	\end{equation}

@@

\begin{equation}
J(\theta) = \frac{1}{m} \sum_{n=1}^{m} [-y^{(i)}}\log(h(x^{(i)}))-(1-y^{(i)})\log(1-h(x^{(i)})]
\end{equation}

>>>>

	\begin{equation}
	x_{0} = (feature)
	\end{equation}

	\begin{equation}
	x_{1} = (feature)^{2}
	\end{equation}

@@

...

\subsubsection{Week 4 - Neural Networks}

	Neural network: more efficient way to learn complex hypothesis.

	Model 1 representation: 
	\begin{itemize}
	\item Dendrite: input wires
	\item Axon: output wire
	\item Cell body: do computations
	\item axon send info to another neuron
	\end{itemize}

	Hypothesis function = activation function

	$\theta$ = parameters = weights

	Layers: first layer: input layer, last layer: output layer, hidden layer: values you don't observe between the input and output.

	Notation: $\Theta$ - matrix of weights controlling function mapping from layer $j$ to layer $j+1$. The dimension is equal to $s_{j+1} \times (s_{j}+1)$; $a_{i}^{(j)}$ - activation of unit $i$ in layer $j$;

### 2019-03-26 Rapport/TG_ITA/Bibliographic_analysis/Coursera.tex
Week 4 assignment

\begin{equation}
J(\theta) = \frac{1}{2m} \sum_{n=1}^{m} (h(x^{(i)})-y^{(i)})^{2} + \lambda\sum_{n=1}^{n} \theta_{j}^{2}
\end{equation}

@@

\begin{equation}
J(\theta) = \frac{1}{m} \sum_{n=1}^{m} [-y^{(i)}}\log(h(x^{(i)}))-(1-y^{(i)})\log(1-h(x^{(i)})]
\end{equation}

\end{document}

>>>>

Regularized cost function:
\begin{equation}
J(\theta) = \frac{1}{2m} \sum_{n=1}^{m} (h(x^{(i)})-y^{(i)})^{2} + \lambda\sum_{n=1}^{n} \theta_{j}^{2}
\end{equation}

@@

...

\subsubsection{Week 4 - Neural Networks}

	Neural network: more efficient way to learn complex hypothesis.

	\textbf{Model 1 representation: }
	\begin{itemize}
	\item Dendrite: input wires
	\item Axon: output wire
	\item Cell body: do computations
	\item axon send info to another neuron
	\end{itemize}

	Hypothesis function = activation function

	$\theta$ = parameters = weights

	Layers: first layer: input layer, last layer: output layer, hidden layer: values you don't observe between the input and output.

	Notation: $\Theta^{j}$ - matrix of weights controlling function mapping from layer $j$ to layer $j+1$. The dimension is equal to $s_{j+1} \times (s_{j}+1)$. The index +1 takes into account the bias added to the inputs and to the computed layer.; $a_{i}^{(j)}$ - activation of unit $i$ in layer $j$;

	\textbf{Model Representation II}
	Vectorized: forward propagation:

	\begin{align}\label{eq:my_eq}
	z^{(j)} = & \Theta^{(j-1)}a^{j-1} \\
	a^{(j)} = & g(z^{(j)})
	\end{align}

Last layer: 	
\begin{align}\label{eq:my_eq}
	z^{(j+1)} = & \Theta^{(j)}a^{j} \\
	a^{(j+1)} = & g(z^{(j+1)}) = h_{\Theta}(x)
	\end{align}

	The away a NN is connected is called an architecture.	
	The first layers computes task of a certain complexity that increases when we go deeper into the network. The last layer usually computes the most demanding task.

	Multiclass Classification
	To classify data into multiple classes, we let our hypothesis function return a vector of values.

	Task 3: Multi-class Classification and Neural Networks (matlab)

	\subsubsection{Week 5}
\end{document}
